---
title: "AMoNet GridSearch"
author: "Loic Verlingue"
date: "19 septembre 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AMoNet_GridSearch}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Set working directory
Where to store the models and do the plotting.
```{r setup}
DIR<-"C:/Users/L_VERLINGUE/Desktop/ModelK/Rpack/AMoNet/"
knitr::opts_knit$set(root.dir = DIR) 
#setwd(DIR)
```

```{r}
# check your directory
print(getwd())
```


# Load (and optionally install) AMoNet package

```{r}

XV<-try(library(AMoNet),silent = T)
#library(AMoNet, lib.loc = "C:/Users/L_VERLINGUE/Documents/R/win-library/3.4/")

if("try-error"%in%class(XV)){
  print("Installing AMoNet from gitlab. Check your ID and pwd")
  devtools::install_git("https://user:password@gitlab.curie.fr/lverling/amonet.git", dependencies = TRUE)
  library(AMoNet)
} else {
  print("AMoNet loaded")
}


```

# Locate your wrapper scripts

```{r}
DirWrapperGS<-system.file('R/RunTCGAopt_HPC.R', package='AMoNet')
print(DirWrapperGS)

DirWrapperDraw<-system.file('R/DrawGridSearch.R', package='AMoNet')
print(DirWrapperDraw)
#file.info(DirWrapperDraw)
```

# On local computer

Set arguments of the wrapper function
The functions is RunTCGAopt(), and the learning hyper-parameters are stored in Default object.

```{r}
# Print RunTCGAopt() arguments or check documentation
print("RunTCGAopt function arguments:")
print(names(formals(RunTCGAopt)))
#?RunTCGAopt
# Print names of hyper-parameters
print("Names of hyper-parameters :")
print(names(Default))
#?Default
```


# Run on local computer
Select hyper-parameters to search, set hyper-parameters you want fix, provide gene queries and other arguments for the building.
Format : --Name_of_argument [space] value 
```{r}
arguments<-"--Param MeanWinit SdWinit --NameProj LUNG_AMoNet_ess --GENESman EGFR MTOR --treatmt --Interval 10 --SelectMECA HALLMARK --organ luad --MinConnect 4 --nblayers 4 --NewNet T --eSS T"
```

Run the worflow iteratively by selecting the number of trials (i.e iteration).
```{r, eval=FALSE}
# set the number of training trials
Ntrials<-10

# run with arguments in a loop
for( i in seq(Ntrials)){
  source(file = DirWrapperGS)
}

```

Draw grid search results (will be stored in tmp/).
```{r, eval=FALSE}
arguments<-"--NameProj LUNG_AMoNet_ess --Validation T"

source(DirWrapperDraw)

```

It is possible to continue with the search of new parameters on the best model from previous search
For that simply keep same NameProj, change Param and NewNet=F.
```{r}
arguments<-"--Param learningrate lambda --NameProj LUNG_AMoNet_ess --organ luad --alpha 1 --iteration 10 --NewNet F --eSS F"
```

Again, run the worflow iteratively.
```{r, eval=FALSE}
# set the number of training trials
Ntrials<-2

# run with arguments in a loop
for( i in seq(Ntrials)){
  source(file = DirWrapperGS)
}

```

Draw grid search results.
```{r, eval=FALSE}
arguments<-"--NameProj LUNG_AMoNet_ess --Validation T"

source(DirWrapperDraw)

```


# Run on HPC
## Connect HPC with ssh

You should adapt:

- the files inst/bash/workflow.sh to set the grid search hyper-parameters and directory
- the firsts lines of inst/R/RunTCGAopt_HPC.R to set the local directory where AMoNet package is installed.
- the variable DirHPC in the following chuck with your HPC directory
*toimprove

```{r, eval=FALSE}

session <- ssh::ssh_connect("lverling@calcsub.curie.fr")
print(session)

#system(DirWorkflow)
DirWorkflow<-system.file("bash/",package = "AMoNet")
DirWorkflow<-file.path(DirWorkflow, list.files(DirWorkflow))

#DirPack<-gsub("AMoNet.*","AMoNet", DirWorkflow)

DirHPC<-"/data/tmp/lverling/AMoNet"

ssh::scp_upload(session, files = c(DirWorkflow, DirWrapperGS, DirWrapperDraw), to = DirHPC,verbose = T)

# set to unix file format - to debug
out<-ssh::ssh_exec_wait(session,command = paste("vi +':w ++ff=unix' +':q' ", DirHPC, gsub(".*bash/","/", DirWorkflow), sep = "") )

#system( paste("dos2unix ", gsub("bash/.*","bash/", DirWorkflow[1]),"*",sep = "")) # ???
#out<-ssh::ssh_exec_wait(session,command = paste("sed -i -e 's/\r\n//g'",DirHPC,"/*",sep = "") )

ssh::ssh_exec_wait(session,command = paste("chmod 777 ",DirHPC,"/*",sep = "") )

# run workflow
#ssh::ssh_exec_wait(session,command = c(paste("cd",DirHPC),"pwd", "sh workflow1.sh"))

outrun<-ssh::ssh_exec_internal(session,command = c(paste("cd",DirHPC),"pwd", "sh workflow.sh"))

rawToChar(outrun$stdout)
rawToChar(outrun$stderr)

#ssh::ssh_exec_wait(session,command = c(paste("cd",DirHPC), "sh workflow.sh"))
#out<-ssh::ssh_exec_wait(session,command = file.path(DirHPC, "workflow.sh"))
#ssh::ssh_exec_wait(session,command = 'sh /data/tmp/lverling/workflow1.sh')

```

```{r, eval=FALSE}
out<-gsub(".torque6.curie.fr","", unlist(strsplit(rawToChar(outrun$stdout),"\n")))

for(i in seq(10)){
  out[length(out)+1]<-paste("TCGATrain.o", gsub("\\[\\]",paste("-",i,sep = ""),out[2]), sep = "")
  
  ssh::scp_download(session, files = file.path(DirHPC, out[length(out)]),to = file.path(getwd(),"tmp"))

}

#ssh::ssh_tunnel(session,port = 22,target = "calcsub.curie.fr:22")

#LF<-ssh::ssh_exec_internal(session,command = c(paste("cd",DirHPC),"ls -l"))


```



#
```{r, eval=FALSE}
ssh::ssh_disconnect(session)
```

