---
title: "AMoNET TCGA"
author: "Loic Verlingue"
date: "31 juillet 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AMoNet_TCGA}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r, loadpack}
library(AMoNet)
if(FALSE){
    print("Loading packages")
    library(reshape2)
    library(parallel)
    library(stringr)
    library(splines)
    library(cgdsr)
    library(survival)
    library(magick)
    library(matrixStats)
    library(survivalROC)
    library(pec)
  }

set.seed(1234)
```

Build AMoNet focused on oncogenic relation between *TP53* and *MTOR* within hallmarks of cancer cells.
Remember to set the number of output values (addOutputs) > 1 to learn on survival data.

## Gene(s) query
```{r, Gene query}
net<-AMoNet(GENESman = c("MTOR","EGFR"))
```

## Build AMoNet 
```{r, build_AMoNet}
net<-build.AMoNet(net, nblayers = 2, MinConnect = 4, RestrictedBuilding = T, MeanWinit = 0.1, SdWinit = 0.1, Phenotypes=GenesSelecHall, MECA=names_MECA, RestrictedBase = T, Interval = 10, Optimizer = "Adam", KeepPhenotypes=T, no_cores = 3, NameProj = "AMoNet_TCGA")
```

## Optionnaly use your own network in AMoNet
See ?prebuilt.AMoNet for information on the format of your network data
```{r, eval = FALSE}
#Don't Run
net<-prebuilt.AMoNet(net, NETall=NULL, MeanWinit = 0.1, SdWinit = 0.1, LSTM=F, Optimizer = Default$Optimizer, Outputs="Output", NameProj="AMoNet_TCGA") 
```

## Plot your network
```{r}
plot(net, network = T)
```

## Load TCGA data
You need connection to internet. Testing connection integrated in cgdsr() package
```{r, loadTCGA}
Species<-union(net$NETall$source_hgnc,net$NETall$target_hgnc)

net<-LoadCleanTCGA(net, Species = Species, Param = "", RestrictUnique = T, organ = "luad")
```

## Create random initial states
```{r}
net<-RandomiStates(net)
#iStates<-net$iStates
```

# Check data dimensions
```{r}
dim(net$Data$y);length(net$Data$MUT);dim(net$iStates); length(Species)

```


## Run optimisation
The train() function takes as input the *AMoNet* object, and optionnaly perturbation data (MUT), treatments (treatm), initial states (iStates), forced initial states (Init) and the labels y. It takes several arguments as hyperparameters, that can be ignored and replaced by the defaults ones. For more details print(Default)

```{r, training}
net<-train.AMoNet(net, y=net$Data$y, MUT=net$Data$MUT, treatmt=NULL,
                         iStates= net$iStates, Init = NULL,
                         ValMut = 100, Ct=NULL, 
                         MiniBatch=16, 
                         iteration=15, 
                         Optimizer="Momentum", 
                         beta1=0.9, beta2=0.999,
                         alpha = 1, lambda = 0.01,
                         Parallelize= T, no_cores = 2,
                         learning_rate=0.001,  
                         LearningRateDecay = NULL,
                         adaptive_iStates= T,
                         Logic = "Sigmoid", Mode = "LAYER", ModeBack = "LAYER",
                         MinStepsForward = 6, 
                         MinStepsBackward = 1,
                         gradClipping=NULL, 
                         LSTM=FALSE, 
                         FixNodes = NULL, 
                         PDF=F, GIF=F, Visualize=NULL) #"Output"
```

# Visualization and interpretation of AMoNet
## Visualize learning phase
```{r}
plot(net$history)
```

Optionnaly you can plot the optimized netowrk
```{r}
plot(net,LEGEND = F, PDF = F,network = T)
```


## Predict
Perform predictions
```{r, predictions}
net<-predict(net)
```

Plot predictions
```{r}
plot(net$Predict)
```


## write your optimized network 
In a .csv file. You can thus use it for other purposes.
```{r, eval = FALSE}
write.AMoNet.network(object = net, file = getwd())
```

```{r}
print("end")
```

