---
title: "AMoNet overview"
author: "Loic Verlingue"
date: "29 juillet 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AMoNet_overview}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

---
```{r}
#install.packages("AMoNet", dependencies=T)
library(AMoNet)
if(TRUE){
    print("Loading packages")
    library(reshape2)
    library(parallel)
    library(stringr)
    library(splines)
    library(cgdsr)
    library(survival)
    library(magick)
    library(matrixStats)
    library(survivalROC)
    library(pec)
  }

set.seed(1234)

```


# Data in AMoNet package
AMoNet comes with 

  * Data to build the network

    + OMNI is a directed protein protein interaction (PPI) database from omnypath [omnipath](http://omnipathdb.org/) pooled with [ACSN](https://acsn.curie.fr/ACSN2/ACSN2.html) and immune models (in house).
    + GenesSelecImmuno are immuno related gene set
    + GenesSelecHall are hallmarks related gene set [MSigDB hallmarks](http://software.broadinstitute.org/gsea/msigdb/)
  
  * Data to train AMoNet
    + LoadCleanTCGA() function to load TCGA data

  * Default hyper-parameters for simulations and training
    + Default are the default hyper-parameters
    + Boundaries are the limit of the hyper-parameter search

The user can set hyper-parameters either in the Default object or in the related functions arguments.

```{r, import Default in global.env()}
#data("Default");data("Boundaries")
head(Default)
length(Default)
```


# Network buiding
## Initiate AMoNet from simple gene(s) query

```{r, eval = FALSE}
net<-AMoNet() # and check in you console to enter the names of your genes
```

Or
```{r}
net<-AMoNet(c("TP53","EGFR"))
#print(names(net))
```


## Build AMoNet network from OMNI molecular interaction database
```{r}
net<-build.AMoNet(net, InteractionBase = OMNI, nblayers = 2, MinConnect = 4, RestrictedBuilding = T, MeanWinit = 0.01, SdWinit = 0.01, Phenotypes = GenesSelecHall, MECA=names_MECA, RestrictedBase = T, Interval = 1, Optimizer = "Adam", KeepPhenotypes=T, no_cores = 1, NameProj = "MyAMoNet")
```


## Plot your network
```{r}
plot(net, network = T)
```

## Simulate with sigmoid update
```{r}
net<-simulate(net, nsim = 10, Logic = "Sigmoid", Parallel = F)
```

## Plot simulation results
```{r}
plot(net,Npat=2)
#summary(net,perPatient = F,Species = NULL)

```


# Alterations of the network
A simple example with 2 patients,  1 single output and artificial mutation data.
```{r}
# prepare mutations data
Species<-union(net$NETall$source_hgnc,net$NETall$target_hgnc)
MUT<-matrix(NA,nrow = 2,ncol = length(Species))
colnames(MUT)<-Species
rownames(MUT)<-c("Pat1","Pat2")#,"Pat3")

# mutate it
# to ways: either descrete ("non NA") or numeric. Numeric is prefered.
if(FALSE){
  MUT[2,"TP53"]<-"mut"
  MUT[2,"EGFR"]<-"mut"
} else{ # or
  MUT[2,"TP53"]<-(-1)
  MUT[2,"EGFR"]<-1
}

print(MUT[,1:10])
```

## Simulation
Simulate and plot simulation for a selected sample (Npat=2)
```{r}
net<-simulate(net, nsim = 10, Logic = "Sigmoid", Mode = "LAYER", MUT=MUT, ValMut = 100, Parallel = F)

plot(net, Npat = 2, ylim=c(0,1))
```

Plot selected species in the network simulation for more that one samples (Npat=1:2)
```{r}
plot(net, Npat = 1:2, PDF = F, ylim=c(0,1), Species = "Output", col=c(2,3))
```


# Optimisation
## Generate outputs
```{r}
Clin<-matrix(c(0.9,0.2),nrow = 1)
colnames(Clin)<-c("Pat1","Pat2")
rownames(Clin)<-"Output"
print(Clin)
```


## Run optimisation
```{r}
net<-train.AMoNet(net,y=Clin,MUT=MUT,ValMut = 100,iteration=10, learning_rate=0.04, PDF=F, GIF=F, Visualize=NULL, Parallelize=F, alpha=0, Optimizer=NULL)
```

# Visualization and interpretation of AMoNet
## Visualize learning phase
```{r}
plot(net$history)

#dim(net$TotAttractors)
#print(net$history)
#plot(net,LEGEND = F, PDF = F)
```

## Relation of phenotype weights to outputs
```{r}
NETall1<-net$history$NETallList[[length(net$history$NETallList)]]
par(mar=c(5, 4, 4, 2) + 0.1)
#par(mar=c(15, 4, 4, 2) + 0.1)
barplot(NETall1[NETall1$Output,"Weights"],names.arg =NETall1[NETall1$Output,1], las=2, cex.names = 0.5)

```

## Predictions
```{r}
net<-predict(net,newMUT = MUT)

plot(net,Npat = 2,PDF = F, ylim=c(0,1),LEGEND = F)

plot(net,Npat = c(1,2),PDF = F,LEGEND = T, ylim=c(0,1), Species = "Output", col=c(2,3))
```

```{r}
print("end")
```


